Model LF

### 2022-11-04 max_dp endogen stød.Rmd
Baily
Commit

>>>>

## Bayli-Chetty function

**of all effects exept prod**

```{r}
sigma=1

### Compensation rates 
comp_r_fag= 0.55
comp_r_dp= 0.52
comp_r_sfc= 0.57

### Micro elasticities
micro_elas_dp= 0.66
micro_elas_dørs= 0.51
micro_elas_fag= 0.36

### Macro elasticities
macro_elas_no_prod= 0.4
macro_elas_prod= 3

### Unemployment rate

ur_fag= 0.05
ur_dp= 0.05
ur_sfc= 0.05

### Case 1

marg_gain_c1= sigma*(comp_r_fag);marg_gain_c1

marg_cost_c1= (micro_elas_fag)/(1-ur_fag); marg_cost_c1

### Case 2

marg_gain_c2= sigma*(comp_r_dp);marg_gain_c2

marg_cost_c2= (micro_elas_dp)/(1-ur_fag); marg_cost_c2

### Case 2

marg_gain_c3= sigma*(comp_r_sfc);marg_gain_c3

marg_cost_c3= (micro_elas_dørs +macro_elas_no_prod )/(1-ur_fag); marg_cost_c3
